\documentclass[12pt]{APA}

\begin{document}
\TITLE{Final Report - Titanic: Machine Learning from Disaster}{Final Report - Group 2}{Maeki Kashana, Miguel Melo Ochoa, Alex Hayet, Francisco Gomez}{\today}{San Diego State University}{CS549 - Machine Learning}{Professor Xin Zhang}
\tableofcontents

\newpage

\section{Introduction and Research Problem}
All details for this project will be provided by a competition titled "Titanic - Machine Learning from Disaster" introduced by kaggle.com (\cite{titanic}).

This following section will provide a brief background and a statement of the problem this project is addressing.




\subsection{Introduction}

This project will build a predictive model that aims to find the type of people who are going to survive the sinking of the Titanic, a well renowned ship that was believed to be "unsinkable" until it hit an iceberg in 1912, resulting in the death of 1502 passengers/crew.

This project will utilize passenger information, such as name, age, gender, socio-economic class, etc., to determine what sorts of groups were more likely to survive than others during the sinking of the Titanic.

This data aforementioned above will be provided by the Kaggle competition and the goal of this project is to engineer code that uses the data to calculate the survival rate of various groups of people.

\subsection{Research Problem}

This project will be creating a predictive model that will dictate the type of individuals that were the most likely to survive the sinking of the Titanic.

To give more detail, this project will be provided with a lot of testing data in order to make predictions on who will survive. In consequence of this data, this team will be able to create a predictive machine learning model that utilizes the data provided for this project to make predictions using various models previously covered in this course. The specific details regarding any related work that relates to this project will be discussed in depth in later sections.

To get more into specifics, this project will utilize these following .csv files to find a solution for this problem: test.csv and train.csv.

\newpage



\section{Related Work}


\newpage



\section{Methodology and Technical Details}

\subsection{Methodology}

\subsection{Technical Details}

\newpage



\section{Experimental Results and Analysis}

\subsection{Experimental Results}

\subsection{Analysis}


\newpage

\section{Conclusion and Future Work}

\subsection{Conclusion}

\subsection{Future Work}


\newpage


\section{Contributions}

\subsection{Maeki Kashana}
\LIST{
\item Significant Contributions to the Final Report
    \LIST { \item Introduced the Research Problem
            \item Discussed, at length, any past work in the course that relates to this project
            \item Summarized findings and suggested possible future directions}
\item Created the README file
}
\subsection{Miguel Melo Ochoa}
\LIST{
\item
}
\subsection{Alex Hayet}
\LIST{
\item
}
\subsection{Francisco Gomez}
\LIST{
\item
}

\printbibliography
\end{document}
